Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-13 paper.tex
Clean up more intro writing

This can be overcome by showing that a scaled physical model test has become
Reynolds number independent, and therefore validation efforts should be relevant
at full-scale.  For scaled physical models, it is of interest how small---since
size, or scale generally correlates inversely with cost---the model can be while
remaining a reliable predictor of full-scale behavior. At the very least, it is
necessary to test at a scale where results can be extrapolated, i.e., changes
are occurring quasi-linearly without dramatic changes in the underlying physical
principles governing the behavior of interest, e.g., power production in the
case of a wind or MHK turbine.

>>>>

Uncertainty from scale effects can potentially be overcome by showing that a
scaled physical model test has become Reynolds number independent, and therefore
validation efforts should be relevant at full scale. It is therefore of interest
how small---since size, or scale generally correlates inversely with cost---the
model can be while remaining a reliable predictor of full-scale behavior. At the
very least, it is necessary to test at a scale where results can be
extrapolated, i.e., changes are occurring quasi-linearly without dramatic
changes in the underlying physical principles governing the behavior of
interest, e.g., power production in the case of a wind or MHK turbine.
